\begin{Parallel}[v]{\colw}{\colx}
{\latin{\noindent	
Ego dixi: In dimídio diérum meórum * vadam ad portas ínferi.\\
Quæsívi resíduum annórum meórum. * Dixi: Non vidébo Dóminum Deum in terra vivéntium.\\
Non aspíciam hóminem ultra, * et habitatórem quiétis.\\
Generátio mea abláta est, et convolúta est a me, * quasi tabernáculum pastórum.\\
Præcísa est velut a texénte, vita mea: dum adhuc ordírer, succídit me: * de mane usque ad vésperam fínies me.\\
Sperábam usque ad mane, * quasi leo sic contrívit ómnia ossa mea:\\
De mane usque ad vésperam fínies me: * sicut pullus hirúndinis sic clamábo, meditábor ut colúmba:\\
Attenuáti sunt óculi mei, * suspiciéntes in excélsum.\\
Dómine, vim pátior, respónde pro me. * Quid dicam, aut quid respondébit mihi, cum ipse fécerit?\\
Recogitábo tibi omnes annos meos * in amaritúdine ánimæ meæ.\\
Dómine, si sic vívitur, et in tálibus vita spíritus mei, corrípies me, et vivificábis me. * Ecce, in pace amaritúdo mea amaríssima:\\
Tu autem eruísti ánimam meam ut non períret: * projecísti post tergum tuum ómnia peccáta mea.\\
Quia non inférnus confitébitur tibi, neque mors laudábit te: * non exspectábunt qui descéndunt in lacum, veritátem tuam.\\
Vivens vivens ipse confitébitur tibi, sicut et ego hódie: * pater fíliis notam fáciet veritátem tuam.\\
Dómine, salvum me fac * et psalmos nostros cantábimus cunctis diébus vitæ nostræ in domo Dómini.
}}
{\vern
{\noindent
I said: In the midst of my days * I shall go to the gates of hell:\\ \\
I sought for the residue of my years. * I said: I shall not see the Lord God in the land of the living.\\ \\
I shall behold man no more, * nor the inhabitant of rest.\\
My generation is at an end, and it is rolled away from me, * as a shepherd’s tent.\\
My life is cut off, as by a weaver: whilst I was yet but beginning, he cut me off: * from morning even to night thou wilt make an end of me.\\
I hoped till morning, * as a lion so hath he broken all my bones:\\ \\
From morning even to night thou wilt make an end of me. * I will cry like a young swallow, I will meditate like a dove:\\
My eyes are weakened * looking upward:\\
Lord, I suffer violence, answer thou for me. * What shall I say, or what shall he answer for me, whereas he himself hath done it?\\
I will recount to thee all my years * in the bitterness of my soul.\\ \\
O Lord, if man’s life be such, and the life of my spirit be in such things as these, thou shalt correct me, and make me to live. * Behold in peace is my bitterness most bitter:\\
But thou hast delivered my soul that it should not perish, * thou hast cast all my sins behind thy back.\\ \\
For hell shall not confess to thee, neither shall death praise thee: * nor shall they that go down into the pit, look for thy truth.\\ \\
The living, the living, he shall give praise to thee, as I do this day: * the father shall make thy truth known to the children.\\
O Lord, save me, and we will sing our psalms all the days of our life * in the house of the Lord.}}

\end{Parallel}



