\subsection{Lesson 4 - From the Treatise of St. Augustine, Bishop of Hippo, Upon the Psalms - On Psalm 63:7}
\begin{Parallel}[v]{\colw}{\colx}
{\latin{\noindent	
Accédet homo ad cor altum, et exaltábitur Deus. \\ \\
Illi dixérunt: Quis nos videbit? \\ \\
Defecérunt scrutántes scrutatiónes, consília mala. \\ \\
Accessit homo ad ipsa consília, passus est se teneri ut homo. \\
 Non enim tenerétur nisi homo, aut viderétur nisi homo, aut cæderétur nisi homo, aut crucifigerétur, aut morerétur nisi homo.\\
 Accessit ergo homo ad illas omnes passiónes, quæ in illo nihil valérent, nisi esset homo. \\ 
 Sed si ille non esset homo, non liberarétur homo. \\
 Accessit homo ad cor altum, id est, cor secretum, 
 objíciens aspéctibus humanis hóminem, servans intus Deum: \\
 celans formam Dei, \\
 in qua æqualis est Patri, \\
 et ófferens formam servi, \\
  qua minor est Patre.\\
\Rbar. Recessit pastor noster, fons aquæ vivæ, ad cujus tránsitum sol obscurátus est:
* Nam et ille captus est, qui captivum tenebat primum hóminem: hódie portas mortis et seras páriter Salvátor noster disrupit.\\ 
\Vbar. Destruxit quidem claustra inférni, et subvértit poténtias diaboli.\\
\Rbar. Nam et ille captus est, qui captivum tenebat primum hóminem: hódie portas mortis et seras páriter Salvátor noster disrupit.
}}
{\vern
{\noindent
We shall attain to thoughts that are very deep: but God shall still be exalted. The enemies of our Lord had communed of laying snares privily; they had said, Who shall see them? They had searched out iniquities; they had accomplished a diligent search. And Man attained even unto (the realization of) their counsels, for the Lord, as Man, suffered Himself to be taken. For He had not been taken at all, unless He had been a Man, or seen, unless He had been a Man, or smitten, unless He had been a Man, or crucified, unless He had been a Man, or have died, unless He had been a Man. Man therefore, He attained unto all those sufferings, which had had nothing in Him, unless He had been a Man. But if He had not been Man, man had not been redeemed. And the Lord as Man attained to thoughts that were very deep, yea, secret; showing the Manhood to the eyes of men, and keeping the Godhead within Him; veiling the form of God, as touching Which, He is Equal to the Father, and manifesting the form of a servant, as touching which, He is inferior to the Father.\\
\Rbar. Our Shepherd, even the Fountain of living waters, is gone from us; He passed away, and the sun was darkened.
* For now hath our Saviour bound him captive, which bound the first man captive; this day hath He burst the gates and bars of death.\\
\Vbar. The bands of hell He hath utterly abolished, and hath done away the power of the devil.\\
\Rbar. For now hath our Saviour bound him captive, which bound the first man captive; this day hath He burst the gates and bars of death.}}

\end{Parallel}