\subsection{Lesson 6}
\begin{Parallel}[v]{\colw}{\colx}
{\latin{\noindent	
Posuérunt custodes milites ad sepúlcrum.\\
 Concussa terra Dóminus resurréxit: \\
 miracula facta sunt talia circa sepúlcrum, ut et ipsi milites, qui custodes advénerant, testes fíerent, si vellent vera nuntiáre.\\
  Sed avarítia illa, quæ captivávit discipulum cómitem Christi, captivávit et militem custodem sepulcri.\\ \\
   Damus, inquiunt, vobis pecúniam: et dícite, quia vobis dormiéntibus venérunt discípuli ejus, et abstulérunt eum.\\ \\ \\ \\
    Vere defecérunt scrutántes scrutatiónes.\\ \\
	 Quid est quod dixísti, o infélix astutia?\\ \\
	 Tantúmne déseris lucem consílii pietátis, et in profúnda versutiæ demérgeris, ut hoc dicas: \\
	 Dícite quia vobis dormiéntibus venérunt discípuli ejus, et abstulérunt eum? \\
	 Dormiéntes testes ádhibes: \\
	 vere tu ipse obdormísti, qui scrutando talia defecísti.
\\ 
\Rbar. Ecce quómodo móritur justus, et nemo pércipit corde: et viri justi tollúntur, et nemo consíderat: a fácie iniquitátis sublátus est justus: 
* Et erit in pace memória ejus.\\ 
\Vbar. Tamquam agnus coram tondénte se obmútuit, et non apéruit os suum: de angustia et de judício sublátus est.\\
\Rbar. Et erit in pace memória ejus.\\
\Rbar. Ecce quómodo móritur justus, et nemo pércipit corde: et viri justi tollúntur, et nemo consíderat: a fácie iniquitátis sublátus est justus: * Et erit in pace memória ejus.
}}
{\vern
{\noindent
So they went, and made the sepulchre sure, sealing the stone, and setting a watch and anon, behold, there was a great earthquake, and the Lord arose. So great wonders were wrought about the sepulchre that the very soldiers, which were put to guard it, were witnesses thereto, if only they would have told the truth. But the same love of money which had made a slave of that disciple who was a companion of Christ, made slaves also of the soldiers that were put to watch His sepulchre. Some of the watch came into the city, and showed unto the chief-priests all the things that were done: and when they were assembled with the elders, and had taken counsel, they gave large money unto the soldiers, saying: Say ye, His disciples came by night and stole Him away while we slept. In good sooth, their diligent search had been accomplished and ended before this. What didst thou say, O stupid cunning? Wast thou indeed so utterly void of the light of godly wisdom, and confounded in the bottomless pit of thine own falsehood as to tell them to say: His disciples came by night, and stole Him away while we slept? Part of the testimony of thine eye-witnesses was that they were asleep at the time: thou thyself wast asleep not to be able to see that on their own testimony, their testimony must have been worthless.
\\
\Rbar. Behold how the righteous dieth, and no man taketh it to heart; and the just are taken away, and none considereth. From the midst of sinners is the righteous translated;
* And his memory is in peace.\\
\Vbar. As a lamb before his shearers is dumb, so He opened not His mouth; He was taken from prison and from judgment.\\
\Rbar. And his memory is in peace.\\
\Rbar. Behold how the righteous dieth, and no man taketh it to heart; and the just are taken away, and none considereth. From the midst of sinners is the righteous translated; * And his memory is in peace.}}

\end{Parallel}