\subsection{Lesson 2 - Lamentations 4}
\begin{Parallel}[v]{\colw}{\colx}
{\latin{\noindent	
Aleph. Quómodo obscurátum est aurum, mutátus est color óptimus, dispersi sunt lápides sanctuárii in cápite ómnium plateárum?
Beth. Fílii Sion íncliti, et amícti auro primo: quómodo reputáti sunt in vasa téstea, opus mánuum fíguli?
Ghimel. Sed et lámiæ nudavérunt mammam, lactavérunt cátulos suos: fília pópuli mei crudélis, quasi strúthio in desérto.
Daleth. Adhǽsit lingua lacténtis ad palátum ejus in siti: párvuli petiérunt panem, et non erat qui frángeret eis.
He. Qui vescebántur voluptuóse, interiérunt in viis: qui nutriebántur in cróceis, amplexáti sunt stércora.
Vau. Et major effécta est iníquitas fíliæ pópuli mei peccáto Sodomórum, quæ subvérsa est in moménto, et non cepérunt in ea manus.
Jerúsalem, Jerúsalem, convértere ad Dóminum Deum tuum.\\
\Rbar. Jerúsalem, surge, et éxue te vestibus jucunditátis: indúere cínere et cilício,
* Quia in te occisus est Salvátor Israël.\\ \\
\Vbar. Deduc quasi torréntem lácrimas per diem et noctem, et non táceat pupílla óculi tui.\\ 
\Rbar. Quia in te occisus est Salvátor Israël.
}}
{\vern
{\noindent
Aleph. How is the gold become dim, the finest colour is changed, the stones of the sanctuary are scattered in the top of every street?
Beth. The noble sons of Sion, and they that were clothed with the best gold: how are they esteemed as earthen vessels, the work of the potter's hands?
Ghimel. Even the sea monsters have drawn out the breast, they have given suck to their young: the daughter of my people is cruel, like the ostrich in the desert.
Daleth. The tongue of the sucking child hath stuck to the roof of his mouth for thirst: the little ones have asked for bread, and there was none to break it unto them.
He. They that were fed delicately have died in the streets; they that were brought up in scarlet have embraced the dung.
Vau. And the iniquity of the daughter of my people is made greater than the sin of Sodom, which was overthrown in a moment, and hands took nothing in her.
Jerusalem! Jerusalem! Return unto the Lord thy God.\\
\Rbar. Arise, O Jerusalem, and put off thy garments of rejoicing: cover thee with sackcloth and ashes
* For the Saviour of Israel hath been slain in the midst of thee.\\
\Vbar. Let thy tears run down like a river day and night, and let not the apple of thine eye cease.\\
\Rbar. For the Saviour of Israel hath been slain in the midst of thee.}}

\end{Parallel}