\subsection{Lesson 1 - Lamentations 3}
\begin{Parallel}[v]{\colw}{\colx}
{\latin{\noindent	
De Lamentatióne Jeremíæ Prophetæ:\\
Heth. Misericordiæ Dómini quia non sumus consúmpti: quia non defecérunt miseratiónes ejus.
Heth. Novi dilúculo, multa est fides tua.
Heth. Pars mea Dóminus, dixit ánima mea: proptérea exspectábo eum.
Teth. Bonus est Dóminus sperántibus in eum, ánimæ quærénti illum.
Teth. Bonum est præstolári cum siléntio salutáre Dei.
Teth. Bonum est viro cum portáverit jugum ab adulescéntia sua.
Jod. Sedébit solitárius, et tacébit: quia levávit super se.
Jod. Ponet in púlvere os suum, si forte sit spes.
Jod. Dabit percutiénti se maxíllam, saturábitur oppróbriis.
Jerúsalem, Jerúsalem, convértere ad Dóminum Deum tuum.\\
\Rbar. Sicut ovis ad occisiónem ductus est, et dum male tractarétur, non apéruit os suum: tráditus est ad mortem,
* Ut vivificáret pópulum suum.\\
\Vbar. Tradidit in mortem ánimam suam, et inter sceleratos reputátus est.\\
\Rbar. Ut vivificáret pópulum suum.}}
{\vern
{\noindent
Lesson from the book of Lamentations:\\
Heth. The mercies of the Lord that we are not consumed: because his commiserations have not failed.
Heth. They are new every morning, great is thy faithfulness.
Heth. The Lord is my portion, said my soul: therefore will I wait for him.
Teth. The Lord is good to them that hope in him, to the soul that seeketh him.
Teth. It is good to wait with silence for the salvation of God.
Teth. It is good for a man, when he hath borne the yoke from his youth.
Jod. He shall sit solitary, and hold his peace: because he hath taken it up upon himself.
Jod. He shall put his mouth in the dust, if so be there may be hope.
Jod. He shall give his cheek to him that striketh him, he shall be filled with reproaches.\\
Jerusalem! Jerusalem! Return unto the Lord thy God.\\ \\
\Rbar. He hath been brought as a lamb to the slaughter, and while he was evil entreated he opened not his mouth: he was delivered up to death
* That he might quicken his people.\\
\Vbar. He hath poured out his soul unto death, and he was numbered with the transgressors.\\
\Rbar. That he might quicken his people.}
}

\end{Parallel}