\subsection{Lesson 5}
\begin{Parallel}[v]{\colw}{\colx}
{\latin{\noindent	
Quo perduxérunt illas scrutatiónes suas, quas perscrutántes defecérunt, ut etiam mortuo Dómino et sepúlto, custodes pónerent ad sepúlcrum? 
Dixérunt enim Pilato: 
Seductor ille: 
hoc appellabátur nómine Dóminus Jesus Christus, ad solatium servórum suórum, quando dicúntur seductores: 
ergo illi Pilato: 
Seductor ille, inquiunt, dixit adhuc vivens: 
Post tres dies resurgam.
Jube itaque custodiri sepúlcrum usque in diem tertium, ne forte veniant discípuli ejus, et furéntur eum, et dicant plebi: Surréxit a mórtuis: et erit novíssimus error pejor priore.
 Ait illis Pilátus: Habetis custódiam, ite, custodíte sicut scitis. 
 Illi autem abeuntes, muniérunt sepúlcrum, signántes lápidem cum custodibus. \\
\Rbar. O vos omnes, qui transítis per viam, atténdite, et vidéte,
* Si est dolor símilis sicut dolor meus.\\
\Vbar. Atténdite, univérsi pópuli, et vidéte dolórem meum.\\
\Rbar. Si est dolor símilis sicut dolor meus.
}}
{\vern
{\noindent
How far did the accomplishment of their diligent search reach? Even to the setting a watch of soldiers at the sepulchre, to guard the Lord, even after He was dead and buried. For they said unto Pilate: Sir, we remember that that deceiver: This was the term by which they designated the Lord Jesus Christ, and the remembrance that He was so named is a sweet consolation to us His servants, when we are called impostors. So they said unto Pilate, that deceiver said, while He was yet alive: After three days I will rise again. Command therefore that the sepulchre be made sure until the third day, lest His disciples come and steal Him away, and say unto the people: He is risen again from the dead: so the last error shall be worse than the first. Pilate said unto them: Ye have a watch; go your way; make it as sure as ye can. So they went and made the sepulchre sure, sealing the stone, and setting a watch.
\\
\Rbar. O all ye that pass by, behold and see;
* If there be any sorrow like unto my sorrow.\\
\Vbar. O all ye nations, behold, and see my sorrow,\\
\Rbar. If there be any sorrow like unto my sorrow.}}

\end{Parallel}